Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-10 journal paper/content/related_work.tex
Related work: removed the coloring, and restored one sentence.

The earlier work by \citet{bergemann1997market,bergemann2000experimentation} studies competition on both prices and quality, and allows for the data externality mentioned above. Specifically, the ``entrant" firm offers a new product of unknown, \gaedit{exogenously determined}, quality, which is ``explored" if and only if the entrant attracts customers. However, because the entrant can only control the prices but not the product itself, the nature of exploration is fundamentally different. First, the goal of exploration is to reveal information about a fixed product. Second, the entrant can only affect the \emph{quantity} of the said information, but not \emph{which} information is being revealed. \gadelete{Third, revealing more information is not necessarily better for the entrant (if the product's quality is actually low).} \gaedit{Third}, the social planner's exploration problem is very different from the firms' \gaedit{so that when one compares competition to the planner, one can only compare outcomes, not the algorithms.}\footnote{The planner faces a two-armed bandit problem, rather than a pricing problem \gaedit{because the planner can directly choose a firm for each agent.}}
% firm, because payments cancel out in social welfare).}

@@

A long line of work from electrical engineering and computer science, starting from
\citet{MultiPlayerMAB-Poor08,MultiPlayerMAB-Liu10,MultiPlayerMAB-Anima11}, \gaedit{focuses on competition for resources, not competition for consumers. Specifically, this literature targets an application} to \emph{cognitive radios}, where multiple radios transmit simultaneously in a shared medium and compete for bandwidth. Each radio chooses channels over time using a multi-armed bandit algorithm. This work studies a repeated game between bandit algorithms, and focuses on designing algorithms which work well in this game, under various assumptions on communication, synchronization and collisions.

>>>>

The earlier work by \citet{bergemann1997market,bergemann2000experimentation} studies competition on both prices and quality, and allows for the data externality mentioned above. Specifically, the ``entrant" firm offers a new product of unknown, exogenously determined, quality, which is ``explored" if and only if the entrant attracts customers. However, because the entrant can only control the prices but not the product itself, the nature of exploration is fundamentally different. First, the goal of exploration is to reveal information about a fixed product. Second, the entrant can only affect the \emph{quantity} of the said information, but not \emph{which} information is being revealed. Third, revealing more information is not necessarily better for the entrant (if the product's quality is actually low). Fourth, the social planner's exploration problem is very different from the firms', so that when one compares competition to the planner, one can only compare outcomes, but not the algorithms.\footnote{The planner faces a two-armed bandit problem, rather than a pricing problem, because the planner can directly choose a firm for each agent.}
% firm, because payments cancel out in social welfare).}

@@

A long line of work from electrical engineering and computer science, starting from
\citet{MultiPlayerMAB-Poor08,MultiPlayerMAB-Liu10,MultiPlayerMAB-Anima11}, focuses on competition for resources, not competition for consumers. Specifically, this literature targets an application to \emph{cognitive radios}, where multiple radios transmit simultaneously in a shared medium and compete for bandwidth. Each radio chooses channels over time using a multi-armed bandit algorithm. This work studies a repeated game between bandit algorithms, and focuses on designing algorithms which work well in this game, under various assumptions on communication, synchronization and collisions.
